Rotations and Insecticide Resistance the story

### 2018-02-13 inst/documents/rotations_notes.Rmd
notes

>>>>

re-read this 
Sternberg & Thomas 2017
Insights from agriculture for the management of insecticide resistance in disease vectors
Because of the situation-specific nature of insecticide resistance management plans, public health may have an advantage over agriculture. Agricultural pest management is concerned with hundreds
of species, and in many cases, detailed data are not available for each pest species (and potential nontarget organisms). Compared to agriculture, public health is concerned with a small number of insect species. This should enable a strongly data-driven approach to selecting resistance management strategies, but in reality, very little is currently known.

• The success of an IRM strategy is highly dependent on ecological and biological specifics; there is not yet a solid evidence base of recommending one strategy over another.
• If control is achieved via the use of multiple tools with diverse modes of action, not only will selection for insecticide resistance be reduced but also, the impact of resistance will likely be less severe. The pending resistance crisis creates an urgent need to develop and implement integrated, multitactic IVM strategies that parallel IPM in agriculture.

To our knowledge, there is only one field trial aimed specifically at testing resistance management strategies against malaria mosquitoes (Penilla et al., 2007). Perhaps worryingly, this trial revealed no clear benefit of either insecticide rotations or mosaics in slowing the spread of resistance when compared to monotherapy. However, these results do not necessarily mean that rotations or mosaics cannot be effective, but rather highlights a critical gap in understanding when, how, and why such strategies might work.

Download papers on modelling oxitech
Insectcide resistance
https://doi.org/10.1093/jee/100.5.1642
https://doi.org/10.1603/029.102.0233

These are not about insecticide resistance (they are about resistance to the gene itself but may have useful pointers)
Alphey2011. Modeling resistance to genetic control of insects
https://doi.org/10.1016/j.jtbi.2010.11.016

Watkinson-Powell2017 Resistance to genetic insect control: Modelling the effects of space
https://doi.org/10.1016/j.jtbi.2016.10.014

Type of fitness cost influences the rate of evolution of resistance to transgenic Bt crops
Looks like could be very interesting :
DOI: 10.1111/1365-2664.12680

Combining the high-dose/refuge strategy and self-limiting transgenic
insects in resistance management- a test in experimental mesocosms 
Zhou2017

submit links to UIs and paper once it is published to :
vectorlearningxchange.com

send Rowland rotation paper to Ian.
